Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
JJP comments

\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
	Ireland} 
\address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
	Pakefield Road, Lowestoft, UK}
\address[3]{\replaced[id=JM]{Sorbonne Université, Faculty of
		Sciences}{Université Pierre et Marie Curie}, 4 Place Jussieu,
	75005 Paris, France}
\address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
	Netherlands}
\address[5]{Aquaculture and Fisheries Group, Wageningen University \& Research,
	Zodiac Building 122, De Elst 1, 6708 WD Wageningen, the Netherlands}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions, we developed a highly resolved spatiotemporal
event-based simulation model incorporating: i) delay-difference
population dynamics, ii) population movement using Gaussian Random Fields to
simulate patchy, heterogeneously distributed populations, and iii) fishery
dynamics for multiple fleet characteristics based on species targeting under an
explore-exploit strategy. This is implemented via a mix of correlated random
walk movement (for exploration) and learned behaviour (for exploitation) phases
of the fisheries.  \\ 
%%
Fifty years of sub-daily fishing was simulated and used to draw inference on
the underlying community structures. We compared inferences based on:
commercial catch, a simulated fixed-site sampling survey design and the true
underlying community. We i) establish the potential limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and then ii) simulated an area closure based on areas defined
from the different data sources at a range of temporal and spatial resolutions.
\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. We conclude from our example framework
application that commercial data, while containing bias, provide a useful tool
for managing catches in mixed fisheries if applied at the correct
spatiotemporal scale. [NEED A LITTLE MORE DETAIL OF THE RESULTS HERE - 2 MORE
SENTENCES ON KEY TAKE-HOME RESULTS]\\
%%
\end{abstract}

@@

An event-based simulation model of a hypothetical fishery was developed as a
software package (\textit{MixFishSim}). The modular approach enabled efficient
computation by allowing for sub-modules implemented on time-scales appropriate
to capture the characteristic of the different processes (Figure 1). The
following sub-modules were included to capture the full system: 1) Population
dynamics, 2) Recruitment dynamics, 3) Population movement, 4) fishery
dynamics.\\

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{\tilde{y},c}$ is the annual recruits in year $y$ for cell $c$. \\

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} \cdot \left(1 -
	\mathrm{e}^{-(F_{c,d} + M_{c,d})}\right) \cdot B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch and fishing
mortality are the sum of those across all fleets and vessels, where $F_{fl, v,
	c, d, p} = E_{fl, v, c, d} \cdot Q_{fl, p} \cdot D_{c, d, p}$ with
$fl$, $v$ and $p$ the fleet, vessel and population respectively and $E$ and $Q$
fishing effort and catchability of the gear, and $D$ is the density of the
population at the location fished. \\

@@

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
\textit{Matérn} covariance structure, where the correlation strength weakens
with distance. This enables us to model the spatial autocorrelation observed in
animal populations where density is more similar in nearby locations
\citep{Tobler1970, F.Dormann2007, Poos2007} and we change the parameters to
implement different spatial structures for the different populations using the
\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
habitat field and combine it with a temporally dynamic thermal tolerance field to
imitate two key drivers of population dynamics. Each population was initialised
at a single location, and subsequently moved across the entire space according
to a probabilistic distribution based on habitat suitability (represented by
the normalised values
from the GRFs), temperature and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{IJ}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{IJ}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{J,p}^2$ is the squared index of
habitat suitability for cell $J$ and population $p$, with $Tol_{J,p,wk}$ the
temperature tolerance for cell $J$ by population $p$ in week $wk$ (see
below). \\

@@

A time-varying temperature covariate changes the interaction between
time and suitable habitat on a weekly time-step. Each population $p$ was
assigned a thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$
so that each cell and population temperature suitability is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma^2_{p}$ the mean and standard deviation of the population
temperature tolerance. \\

@@

Fleet dynamics can be broadly categorised into three components: fleet
targeting - that determined the fleet catch efficiency and preference towards a
particular species; trip-level decisions, that determines the initial location
to be fished at the beginning of a trip; and within-trip decisions, that
determines movement from one fishing spot to another within a trip. An
explore-exploit type strategy was implemented in the model that combined these
three components for individual vessels to maximise their catch from an unknown
resource distribution \citep{Bailey2018}. The decision to use an individual
based model for fishing vessels was taken because fishers are heterogeneous in
their location choice behaviour due to different objectives, risk preference
and targeting preference \citep{VanPutten2012a}. Therefore in the simulations
fleet dynamics reflect individual experiences rather than pre-defined group
dynamics.

@@

For our implementation of a random walk directional change is based on a
negatively correlated circular distribution where a favourable fishing ground
is likely to be ``fished back over" by the vessel returning in the direction it
came from.  The step length (i.e. the distance travelled from the current to
the next fishing location) is determined by relating recent
fishing success, measured as the summed value of fish caught (revenue, $Rev$);
\begin{equation}
Rev = \sum_{p=1}^{P} \replaced[id=PD]{L}{C}_{p} \cdot Pr_{p} 
\end{equation}
where $L_{p}$ is landings of a population $p$, and $Pr_{p}$ price of a
population. All species prices were kept the same across fleets and seasons.
Here, when fishing is successful vessels remain in a similar location and
continue to exploit the local fishing grounds. When unsuccessful, they move
some distance away from the current fishing location.  The movement distance
retains some degree of stochasticity, that can be controlled separately, but is
determined by the relationship: 
\begin{equation}
	StepL = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right)} \cdot Rev
\end{equation}
Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
shape of the step function in its relation to revenue, so that, a step from
(x1,y1) to (x2, y2) is defined by:
\begin{equation}
	\begin{split}
 (x2, y2) =  & x1 + L \cdot \cos \left(\frac{\pi \cdot Br}{180}\right), \\
             & y1 + L \cdot \sin \left(\frac{\pi \cdot Br}{180}\right) \\	
 with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
	\end{split}
\end{equation}
where $L$ is the step length, $k$ the concentration parameter from the von
Mises distribution that we correlate with the revenue so
that $k = (Rev + 1 / RefRev) * max_{k}$, where $max_{k}$ is the maximum
concentration value, $k$, and $RefRev$ is parametrised as for $\beta_{3}$ in
the step length function.

@@

It can be seen from a single vessels movements during a trip that the vessel
exploits three different fishing grounds, each of them multiple times (Figure
\ref{fig:mv}(A)), while across several trips fishing grounds that are further
apart are fished (Figure \ref{fig:mv} (B)). These different locations relate to
areas where the highest revenue were experienced, as shown by
\added[id=PD]{Figure} \ref{fig:13}, where several vessels tracks are
overlaid on the revenue field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot
Q_{s,c}$$

@@

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
that may differ from the underlying populations [[\citep{Gillis2008}]]. As
such, we favoured a minimum realistic model of the fish populations
\citep{Plaganyi2014} taking account of environmental but not demographic
stochasticity, while incorporating detailed fishing dynamics that take account
of different drivers in a mechanistic way.  \\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account \added[id=CM]{(Figures X,Y,Z)}. \\

Our simulation shows that, despite biases introduced through the fishing
process, the commercially derived data could still inform on the key spatial
patterns in the community structures where the fisheries occurred, which was
spatially limited due to the ``hotspots" of commercially valuable species being
fished. Similarly, despite the even spatial coverage the survey was able to
capture some of the same spatial patterns as the real population, but missed
others due to gaps between survey stations limiting spatial and temporal
coverage \added[id=CM]{(Figures X,Y,Z)}. This provides a challenge when
modelling unsampled areas in inferring species distribution maps, though these
limitations may be overcome by understanding the relationship between the
species and habitat covariates where these are known at unsampled locations
\citep{Robinson2011}. \\

@@

%% the tikz figure
\clearpage
\input{Process_model.tex}
%\begin{comment}
\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Simulated spatial dynamics - the four populations abundance
		(log+1) at four time steps.
		}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		showing weekly and seasonal patterns in exploitation.
		Individual years and the light grey lines, the mean of all
		years the thick black line}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
	single vessel during a trip overlaid on the relative value of a fishing
	site; (B) the fishing locations of the vessel over several trips (value
field changes over the period so not shown); (C) the locations of multiple
vessels from the same fleet overlaid on the value field, (D) the realised step
distance and turning angles for a single vessel over the simulation}
	\label{fig:mv}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/vessel_move_value}
	\caption{movement of a fleet over a single trip reference overlaid on the
		value field (i.e. sum of the population abundance x catchability x value}
	\label{fig:13}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios effect on fishing mortality
		trends. Line colour denotes the timescale, while linestyle
		denotes the spatial resolution.}
	\label{fig:3}
\end{figure}

>>>>

\address[1]{Galway-Mayo Institute of Technology (GMIT), Dublin Road, Galway,
	Ireland} 
\address[2]{Centre for Environment, Fisheries and Aquaculture Science (Cefas),
	Pakefield Road, Lowestoft, UK}
\address[3]{Sorbonne Université, Faculty of Sciences, 4 Place Jussieu, 75005
	Paris, France}
\address[4]{Wageningen Marine Research, Haringkade 1 1976 CP IJmuiden,
	Netherlands}
\address[5]{Aquaculture and Fisheries Group, Wageningen University \& Research,
	Zodiac Building 122, De Elst 1, 6708 WD Wageningen, the Netherlands}

@@

%%
To understand how data resolution impacts inference on mixed fisheries
interactions, we developed a highly resolved spatiotemporal discrete-event
simulation model incorporating: i) delay-difference population dynamics, ii)
population movement using Gaussian Random Fields to simulate patchy,
heterogeneously distributed populations, and iii) fishery dynamics for multiple
fleet characteristics based on species targeting under an explore-exploit
strategy. This is implemented via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries.
\\ 
%%
Fifty years of sub-daily fishing was simulated and used to draw inference on
the underlying community structures. We compared inferences based on:
commercial catch, a simulated fixed-site sampling survey design and the true
underlying community. We i) establish the potential limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and then ii) simulated an area closure based on areas defined
from the different data sources at a range of temporal and spatial resolutions.
\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. We conclude from our example framework
application that commercial data, while containing bias, provide a useful tool
for managing catches in mixed fisheries if applied at the correct
spatiotemporal scale. [NEED A LITTLE MORE DETAIL OF THE RESULTS HERE - 2 MORE
SENTENCES ON KEY TAKE-HOME RESULTS]\\
%%
\end{abstract}

@@

A Discrete-event simulation (DES) model of a hypothetical fishery was developed
as a software package (\textit{MixFishSim}). The modular approach enabled
efficient computation by allowing for sub-modules implemented on time-scales
appropriate to capture the characteristic of the different processes (Figure
1). The following sub-modules were included to capture the full system: 1)
Population dynamics, 2) Recruitment dynamics, 3) Population movement, 4)
fishery dynamics.\\

@@

The basic population level processes were simulated using a modified two-stage
Deriso-Schnute delay difference model which models the fish populations in
terms of aggregate biomass of recruits and mature components rather than
keeping track of individuals\citep{Deriso1980, Schnute1985, Dichmont2003}. A
daily time-step was chosen to discretise continuous population processes on a
biologically relevant and computationally tractable timescale. Population
biomass growth was modelled as a function of previous recruited biomass,
intrinsic population growth and recruitment functionally linked to the adult
population size.  Biomass for each cell $c$ was incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}): 
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot \mathrm{e}^{-Z_{c,d}} - \rho \cdot
	\mathrm{e}^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot \mathrm{e}^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $\mathrm{e}^{-K}$
when $K$ is the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y},d}$ is the annual recruits in year $y$ and day $d$ for cell
$c$. \\

Mortality $Z_{c,d}$ can be decomposed to natural mortality, $M_{c,d}$, and
fishing mortality, $F_{c,d}$, where both $M_{c,d}$ and $F_{c,d}$ are
instantaneous rates with $M_{c,d}$ fixed and $F_{c,d}$ calculated by solving
the Baranov catch equation \citep{Hilborn1992b} for $F_{c,d}$:
\begin{equation}
C_{c,d} = \frac{F_{c,d}}{F_{c,d} + M_{c,d}} \cdot \left(1 -
	\mathrm{e}^{-(F_{c,d} + M_{c,d})}\right) \cdot B_{c,d}
\end{equation}
where $C_{c,d}$ is the summed catch from the fishing model across all fleets
and vessels in cell $c$ for the population during the day $d$, and $B_{c,d}$
the daily biomass for the population in the cell. Here, catch is the sum of
those across all fleets and vessels, $C_{c, d} =
\sum\limits_{fl=1}^{fl}\sum\limits_{v=1}^{v} E_{fl, v, c, d} \cdot Q_{fl} \cdot
D_{c, d}$ with $fl$ and $v$ the fleet and vessel respectively and
$E_{fl,v,c,d}$ and $Q_{fl}$ fishing effort and catchability of the gear, and
$D_{c,d}$ is the density of the population at the location fished. \\

@@

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
\textit{Matérn} covariance structure, where the correlation strength weakens
with distance. This enables us to model the spatial autocorrelation observed in
animal populations where density is more similar in nearby locations
\citep{Tobler1970, F.Dormann2007, Poos2007} and we change the parameters to
implement different spatial structures for the different populations using the
\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
habitat field and combine it with a temporally dynamic thermal tolerance field to
imitate two key drivers of population dynamics. Each population was initialised
at a single location, and subsequently moved across the entire space according
to a probabilistic distribution based on habitat suitability (represented by
the normalised values
from the GRFs), temperature and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{I,J}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{I,J}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{c,p}^2$ is the squared index of
habitat suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
temperature tolerance for cell $c$ by population $p$ in week $wk$ (see
below). \\

@@

A time-varying temperature covariate changes the interaction between time and
suitable habitat on a weekly time-step. Each population $p$ was assigned a
thermal tolerance with mean, $\mu_{p}$ and variance, $\sigma^2_{p}$ so that
each cell and population temperature suitability is defined that:
\begin{equation}
	Tol_{c, p, wk} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c, wk} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, wk}$ is the tolerance of population $p$ for cell $c$ in week
$wk$, $T_{c, wk}$ is the temperature in the cell given the week and $\mu_{p}$
and $\sigma^2_{p}$ the mean and standard deviation of the population
temperature tolerance. \\

@@

Fleet dynamics can be broadly categorised into three components: fleet
targeting - that determined the fleet catch efficiency and preference towards a
particular species; trip-level decisions, that determines the initial location
to be fished at the beginning of a trip; and within-trip decisions, that
determines movement from one fishing spot to another within a trip. An
explore-exploit type strategy was implemented in the model that combined these
three components for individual vessels to maximise their catch from an unknown
resource distribution \citep{Bailey2018}. The decision to use an individual
based model for fishing vessels was taken because fishers are heterogeneous in
their location choice behaviour due to different objectives, risk preference
and targeting preference \citep{VanPutten2012a, Boonstra2015}. Therefore fleet
dynamics are emergent from individual dynamics rather than pre-defined group
dynamics.

@@

For our implementation of a random walk directional change is based on a
negatively correlated circular distribution where a favourable fishing ground
is likely to be ``fished back over" by the vessel returning in the direction it
came from.  The step length (i.e. the distance travelled from the current to
the next fishing location) is determined by relating recent
fishing success, measured as the summed value of fish caught (revenue, $Rev$);
\begin{equation}
Rev_{c,d} = \sum_{p=1}^{P} L_{c,d,p} \cdot Pr_{p} 
\end{equation}
where $L_{c,d,p}$ is landings of a population $p$, and $Pr_{p}$ price of a
population. All species prices were kept the same across fleets and seasons.
Here, when fishing is successful vessels remain in a similar location and
continue to exploit the local fishing grounds. When unsuccessful, they move
some distance away from the current fishing location.  The movement distance
retains some degree of stochasticity, that can be controlled separately, but is
determined by the relationship: 
\begin{equation}
	Le = \mathrm{e}^{log(\beta_{1}) + log(\beta_{2}) -
		\left(log\left(\frac{\beta_{1}}{\beta_{3}}\right)\right) \cdot Rev
} 
\end{equation}
Where $\beta_{1}$, $\beta_{2}$ and $\beta_{3}$ are parameters determining the
shape of the step function in its relation to revenue, so that, a step from
(x1,y1) to (x2, y2) is defined by:
\begin{equation}
	\begin{split}
 (x2, y2) =  & x1 + Le \cdot \cos \left(\frac{\pi \cdot Br}{180}\right), \\
             & y1 + Le \cdot \sin \left(\frac{\pi \cdot Br}{180}\right) \\	
 with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
	\end{split}
\end{equation}
where $Le$ is the step length, $k$ the concentration parameter from the von
Mises distribution that we correlate with the revenue so that $k = (Rev + 1 /
RefRev) \cdot max_{k}$, where $max_{k}$ is the maximum concentration value,
$k$, and $RefRev$ is parametrised as for $\beta_{3}$ in the step length
function.

@@

It can be seen from a single vessels movements during a trip that the vessel
exploits three different fishing grounds, each of them multiple times (Figure
\ref{fig:mv}(A)), while across several trips fishing grounds that are further
apart are fished (Figure \ref{fig:mv} (B)). These different locations relate to
areas where the highest revenue were experienced, as shown by Figure
\ref{fig:mv} (D), where several vessels tracks are overlaid on the revenue
field, i.e. $$\sum^c_{c=1}\sum^s_{s=1} B_{s,c} \cdot Q_{s,c}$$

@@

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE; \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
that may differ from the underlying populations, as identified by
\cite{Gillis2008}. As such, we favoured a minimum realistic model of the fish
populations \citep{Plaganyi2014} taking account of environmental but not
demographic stochasticity, while incorporating detailed fishing dynamics that
take account of different drivers in a mechanistic way.  \\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account (Figures X,Y,Z). \\

Our simulation shows that, despite biases introduced through the fishing
process, the commercially derived data could still inform on the key spatial
patterns in the community structures where the fisheries occurred, which was
spatially limited due to the ``hotspots" of commercially valuable species being
fished. Similarly, despite the even spatial coverage the survey was able to
capture some of the same spatial patterns as the real population, but missed
others due to gaps between survey stations limiting spatial and temporal
coverage (Figures X,Y,Z). This provides a challenge when
modelling unsampled areas in inferring species distribution maps, though these
limitations may be overcome by understanding the relationship between the
species and habitat covariates where these are known at unsampled locations
\citep{Robinson2011}. \\

@@

%% the tikz figure
\clearpage
\input{Process_model.tex}
%\begin{comment}
\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Spatial density (log abundance) for each of the four
		populations at four time steps. The darker the colour the
		greater the density of the population. Note that you can see
		the diagonal isotropic patterns in populations 2 and 3 and
		concentrated spawning areas in the second row of the panels
		(t=18) }
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years and the light grey
		lines, the mean of all years the thick black line}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
		single vessel during a trip overlaid on the relative value of a
		fishing site; (B) the fishing locations of the vessel over
		several trips (value field changes over the period so not
		shown). Note that the field is wrapped on a torus so that
		distances between opposite side of the spatial domain are
		considered next to each other, hence apparent large movements;
		(C) the locations of multiple vessels from the same fleet
		overlaid on the value field, (D) the realised step distance and
		turning angles for a single vessel over the simulation}
	\label{fig:mv}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../analysis/F_trendsREV}
	\caption{Comparison of closure scenarios effect on fishing mortality
		trends. Line colour denotes the timescale, while linestyle
		denotes the spatial resolution. The vertical dashed line
		indicates the onset of the spatial closures.}
	\label{fig:3}
\end{figure}

### 2019-09-17 write_up/parameter_tables.tex
JJP comments

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Habitat model}} \\
		\hline
		a & b & c \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		the population & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & decay rate for population movement & - \\
		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
		$c$ at week $wk$ & - \\
		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
		\hhline{===}
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		StepL & Step length for vessel & euclidean distance \\
		Br & Bearing & degrees \\
		$k$ & Concentration parameter for Von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Habitat model}} \\
		\hline
		a & b & c \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		the population & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & decay rate for population movement & - \\
		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
		for population $p$ & - \\
		$d_{I,J}$ & euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
		\hhline{===}
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		Le & Step length for vessel & euclidean distance \\
		Br & Bearing & degrees \\
		$k$ & Concentration parameter for Von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}
